\subsection{Technologies}
The following technologies will be used in the implementation of the system:\\ \\
{\bfseries Client Side:}
\begin{itemize}
	\item AngularJS: \\ \\
	AngularJS is a technology, used on the client side to make it possible to serve a dynamic view in web-applications. This technology is also fully extensible, hence allowing it to work well with other libraries.
	\item Angular Material: \\ \\
	Angular Material is a framework supported by Google. The goal of the framework is to provide an efficient and simple way to implement Google's Material Design Guidelines.
	\item jQuery: \\ \\
	jQuery is a very powerful JavaScript library which makes the use of animations, document manipulation, AJAX, etc. much simpler to handle. jQuery is an API that works across multiple browsers, providing compatibility over multiple platforms.
	\item D3: \\ \\
	D3 is a JavaScript library which is used to manipulate documents which are based on data. D3 is used to visually represent the data contained within the document.
\end{itemize}

{\bfseries Server Side:}
\begin{itemize}
	\item Node.js:\\ \\ 
	Node.js is an API which is used to build scalable, and fast network applications with ease. The API is inherently asynchronous to increase server-side performance.
	\item Node Package Manager:\\ \\
	Node Package Manager is used by node.js to manage the packages which will be used on the server. This allows a uniform execution environment to exist.
	\item MongoDB: \\ \\
	MongoDB is a document database based on the NoSQL movement. It allows a system to be agile, whilst still maintaining scalability and performance.
	\item mongoose \\ \\
	Mongoose will provide us with connection to the database. Schemers will provide us with consistent data in the database.
	\item ldapjs \\ \\
	This will allow us to connect to the client database and obtain the user data.
\end{itemize}
{\bfseries Mobile Application}
\begin{itemize}
	\item PhoneGap:\\ \\
	PhoneGap is a utility that creates mobile application from web based technologies. This utility integrates effectively with all the aforementioned technologies in order to produce a mobile, responsive application for smart phones.
\end{itemize}
{\bfseries Testing and Integration}
\begin{itemize}
	\item Nodeunit:\\ \\
	Nodeunit will be used to write unit tests for the server side node modules.
	\item Jasmine and Karma:\\ \\
	These technologies will be used to perform tests on behavioral JavaScript, as written with the use of AngularJS.
	\item Travis CI:\\ \\
	Travis CI will be used to integrate functions based on their appropriate unit tests.
\end{itemize}